Simulation Figures for Genome Biology (simulations)

### 2018-07-19 manuscript_figures/manuscript_figures_sims.Rmd
Redo all simulation figures to better match other figures

# set alpha cutoff for plots that are fixed at a certain value of alpha
alpha <- 0.10

methodset <- c("bonf", "bh", paste0("ihw-a", round(alpha * 100)),
               "qvalue", "bl-df03", "lfdr",
               "scott-empirical", "scott-theoretical", "ashq")
```

@@

First, we load summaries for all simulations results.

```{r}
summary_file <- paste0("allres_alpha", 100*alpha, ".rds")

if (file.exists(summary_file)) {
    res <- readRDS(summary_file)
} else {
    res_files <- list.files(path, "\\.rds$", full.names = TRUE)
    res <- lapply(res_files, function(x) {
        zz <- readRDS(x)
        zz <- plotsim_standardize(zz, alpha = alpha)
        zz <- dplyr::select(zz, rep, blabel, key, alpha, value)

        zz <- dplyr::group_by(zz, blabel, key, alpha)
        zz <- dplyr::summarize(zz,
                               se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
                               q10 = quantile(value, .1, na.rm = TRUE),
                               q90 = quantile(value, .9, na.rm = TRUE),
                               med_value = median(value, na.rm = TRUE),
                               mean_value = mean(value, na.rm = TRUE),
                               nNA = sum(is.na(value)))
        dplyr::ungroup(zz)
    })
    names(res) <- gsub("\\.rds$", "", basename(res_files))
    saveRDS(res, summary_file)
}

## merge all simulation summaries
res <- bind_rows(res, .id = "setting")

## create shorter simulation setting labels
res <- dplyr::mutate(res, dist = gsub(".*?-benchmark-(.*)", "\\1", setting),
                     setting = gsub("(.*?)-benchmark-.*", "\\1", setting))

## only use subset of methods for plotting
res <- dplyr::filter(res, blabel %in% methodset)
res <- dplyr::rename(res, Method = blabel)

## remove suffixes for unused tuning parameters
res <- dplyr::mutate(res, Method = gsub("-df03", "", Method),
                     Method = gsub("(-a)(.*)", "", Method))
methodset <- gsub("-df03", "", methodset)
methodset <- gsub("(-a)(.*)", "", methodset)

## add candy color scheme from datasets/R/colorPalette.R
res <- dplyr::left_join(res, candycols, by = "Method")

## treat methods as factors for forced ordering
res <- dplyr::mutate(res, Method = factor(Method, levels = methodset))
```

@@

```{r}
res_nullset <- dplyr::filter(res, setting == "null")
res_nullset <- dplyr::mutate(res_nullset, dist = factor(dist, levels = c("gaussian", "t5", "chisq4")))
res_nullset <- tidyr::complete(res_nullset, setting, Method, dist, key)

col <- as.character(res_nullset$col)
names(col) <- as.character(res_nullset$Method)
```

For null simulations, rather than the false discovery rate, we take a look at the number
false positives since the FDR will be 1 if any rejections are made.

In these plots, `ashq`, `scott-theoretical` and `scott-theoretical` are excluded for the Chi-Squared
simulation settings.

```{r, fig.width = 8, fig.height = 5}
dplyr::filter(res_nullset, key == "rejectprop") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se)) + 
    facet_grid(. ~ dist) +
    scale_color_manual(values = col, guide = FALSE) +
    scale_y_continuous("Average % Rejected Tests", breaks = seq(0, 1, .01), labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Rejected proportion in null simulations (average over 100 replications)") 
```

Additionally, we take a look at the FWER (the proportion of simulation replicates out of 100
with at least one rejection).

```{r, fig.width = 8, fig.height = 5}
dplyr::filter(res_nullset, key == "FWER") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    scale_color_manual(values = col, guide = FALSE) +
    facet_grid(. ~ dist) +
    scale_y_continuous("FWER", breaks = seq(0, 1, .2), labels = scales::percent) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Proportion of replications with at least one false positive (over 100 replications)") 
```

Finally, we plot the TNR as was done for the yeast in silico experiments/simulations.

```{r, fig.width = 8, fig.height = 5}
gp <- dplyr::filter(res_nullset, key == "TNR") %>%
    filter(! (Method == "ashq" & dist == "chisq4"),
           ! (grepl("scott", Method) & dist == "chisq4")) %>%
    ggplot(aes(x = Method, y = mean_value, color = Method)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se)) + 
    facet_grid(. ~ dist) +
    scale_y_continuous("TPR", labels = scales::percent) +
    scale_color_manual(values = col, guide = FALSE) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    ggtitle("Average TNR (over 100 replications)") 
gp

ggsave(file.path(outdir, "FigureSsim-null.pdf"), gp, width = 8, height = 5)
```

# Informative and Non-Informative Covariates

```{r}
res_covset <- dplyr::filter(res, grepl("informative", setting))
res_covset <- dplyr::mutate(res_covset, dist = factor(dist,
                                                      levels = c("gaussian", "t11", "t5", "chisq4"),
                                                      labels = c(expression("Noise: " * N(0, 1)),
                                                                 expression("Noise: " * t[11]),
                                                                 expression("Noise: " * t[5]),
                                                                 expression("Noise: " * {chi^2}[4]))))
res_covset <- dplyr::mutate(res_covset, setting = factor(setting,
                                                         levels = c("noninformative", "informative-step",
                                                                    "informative-cubic", "informative-sine")))
res_covset <- tidyr::complete(res_covset, setting, Method, dist, key)
```

We use scatterplots to look at the FDR and TPR values.

```{r, fig.width = 11, fig.height = 4.5}
## looking at FDR vs TPR
col <- as.character(res_covset$col)
names(col) <- as.character(res_covset$Method)

## looking at noninformative vs. informative (cubic)
dplyr::select(res_covset, Method, setting, dist, key, mean_value, se) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("TPR"),
                  ! Method %in% c("ashq", "bonf")) %>%
    dplyr::mutate(plus1se = mean_value + se, minus1se = mean_value - se) %>%
    dplyr::select(-se) %>%
    tidyr::gather(metric, value, mean_value, plus1se, minus1se) %>%
    tidyr::unite(metric, c("setting", "metric")) %>%
    tidyr::spread(metric, value) %>%
    ggplot(aes(x = noninformative_mean_value, y = `informative-cubic_mean_value`, color = Method)) +
    geom_errorbar(aes(ymin = `informative-cubic_minus1se`, ymax = `informative-cubic_plus1se`), width = 0) +
    geom_errorbarh(aes(xmin = noninformative_minus1se, xmax = noninformative_plus1se), height = 0) + 
    ##geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 1, scales = "free", labeller = labeller(dist = label_parsed)) +
    scale_x_continuous(labels = scales::percent) + 
    scale_y_continuous(labels = scales::percent) + 
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    ggtitle("Mean TPR for Informative and Noninformative Simulations") 
```

```{r}
## looking at noninformative vs. informative (cubic)
pfdr <- dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("FDR")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    geom_vline(xintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 2, scales = "free", labeller = labeller(dist = label_parsed)) +
    scale_x_continuous("FDR w/ Noninformative Covariate", labels = scales::percent, limits = c(0, 1)) + 
    scale_y_continuous("FDR w/ Informative Covariate (cubic)", labels = scales::percent, limits = c(0, 1)) + 
    ggtitle("FDR (Informative and Noninformative Sims)")

## looking at noninformative vs. informative (cubic)
ptpr <- dplyr::select(res_covset, Method, setting, dist, key, mean_value) %>%
    dplyr::filter(setting %in% c("noninformative", "informative-cubic"),
                  key %in% c("TPR")) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, color = Method)) +
    geom_abline(color = "blue", lty = 2, alpha = 1/3) +
    geom_vline(xintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) +
    geom_point(alpha = 1) +
    scale_color_manual(values = col) +
    facet_wrap( ~ dist, nrow = 2, scales = "free", labeller = labeller(dist = label_parsed)) +
    scale_x_continuous("TPR w/ Noninformative Covariate", labels = scales::percent, limits = c(0, 1)) + 
    scale_y_continuous("TPR w/ Informative Covariate (cubic)", labels = scales::percent, limits = c(0, 1)) + 
    ggtitle("TPR (Informative and Noninformative Sims)") 
```

We can plot both FDR and TPR together.

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr,
                rel_widths = c(1, 1.4), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-noise.pdf"), gp, width = 11, height = 4.5)

gp_zoom <- plot_grid(pfdr + coord_cartesian(c(0, .2), c(0, .2)) + guides(color = FALSE, linetype = FALSE),
                     ptpr + coord_cartesian(c(.6, 1), c(.6, 1)), rel_widths = c(1, 1.4), labels = LETTERS[1:2])
gp_zoom

ggsave(file.path(outdir, "FigureSsim-noise-zoom.pdf"), gp_zoom, width = 11, height = 4.5)
```

# Varying Null Proportions

Next, we subset on simulation results that look at varying the null proportions.

```{r}
res_pi0set <- dplyr::filter(res, grepl("varyingpi0", setting))
res_pi0set <- dplyr::rename(res_pi0set, pi0 = dist)
res_pi0set <- dplyr::mutate(res_pi0set, pi0 = as.numeric(gsub("nullprop", "", pi0)))
res_pi0set <- tidyr::complete(res_pi0set, setting, Method, pi0, key)
res_pi0set <- dplyr::mutate(res_pi0set, setting = factor(setting, levels = c("varyingpi0", "varyingpi0-lowsignal"),
                                                         labels = c("high signal", "low signal")))
```

We take a look at the TPR and FDR as function of the proportion of null hypotheses.

```{r}
## looking at FDR vs TPR
col <- as.character(res_pi0set$col)
names(col) <- as.character(res_pi0set$Method)
lty <- as.character(res_pi0set$lty)
names(lty) <- as.character(res_pi0set$Method)

## including SE to show variability in FDRR
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average FDR Across Varying Null Proportion")

## including SE to show variability in FDRR
ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 1/6, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), alpha = 1) +
    geom_point(alpha = 1, position = position_dodge(width = .01)) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Average TPR Across Varying Null Proportion")
```

Again, we can plot both FDR and TPR together.

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE),
                ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 15, height = 7.5)

## trimmed ranges
gp_zoom <- plot_grid(pfdr + coord_cartesian(ylim = c(0, .25)) + guides(color = FALSE, linetype = FALSE),
                     ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp_zoom

ggsave(file.path(outdir, "FigureSsim-nullprop-zoom.pdf"), gp_zoom, width = 15, height = 7.5)
```

# Unimodal Effect Sizes

Next, we subset on simulation results that look at varying unimodal simulation settings
that were used in the simulations of the ASH paper.

```{r}
res_unimodal <- dplyr::filter(res, grepl("varyinges", setting), dist != "bimodal")
res_unimodal <- dplyr::rename(res_unimodal, signal = dist)
res_unimodal <- tidyr::separate(res_unimodal, setting, c("setting", "dist"), by = "-", fill = "right")
res_unimodal$dist[is.na(res_unimodal$dist)] <- "gaussian"
res_unimodal <- tidyr::complete(res_unimodal, setting, Method, dist, signal, key)
res_unimodal <- dplyr::mutate(res_unimodal, dist = factor(dist,
                                                          levels = c("gaussian", "t", "chisq"),
                                                          labels = c(expression("Noise: " * N(0, 1)),
                                                                 expression("Noise: " * t[11]),
                                                                 expression("Noise: " * {chi^2}[4]))))
```

We take a look at the TPR and FDR as function of the informativeness.

```{r, fig.width = 12, fig.height = 7.5}
## looking at FDR vs TPR
col <- as.character(res_unimodal$col)
names(col) <- as.character(res_unimodal$Method)
lty <- as.character(res_unimodal$lty)
names(lty) <- as.character(res_unimodal$Method)

>>>>

methodset <- c("bonf", "bh", "ihw", "qvalue", "bl-df03", "lfdr",
               "scott-empirical", "scott-theoretical", "ashq")
```

@@

First, we load summaries for all simulations results at significance thresholds
between 0.01 and 0.10. This process can take a long time (approximately 40 minutes
per alpha cutoff) because of the large number of simulation settings that must be
read in and summarized. Ideally, this initial step should be run externally separate
from this Rmd (by default, the following code chunk will not be run).

```{r, eval = FALSE}
for (ia in 1:10) {
    summary_file <- paste0("allres_alpha", 100*alpha, ".rds")
    if (!file.exists(summary_file)) {
        res_files <- list.files(path, "\\.rds$", full.names = TRUE)
        res <- lapply(res_files, function(x) {
            zz <- readRDS(x)
            zz <- plotsim_standardize(zz, alpha = alpha)
            zz <- dplyr::select(zz, rep, blabel, key, alpha, value)
            zz <- dplyr::group_by(zz, blabel, key, alpha)
            zz <- dplyr::summarize(zz,
                                   se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
                                   q10 = quantile(value, .1, na.rm = TRUE),
                                   q90 = quantile(value, .9, na.rm = TRUE),
                                   med_value = median(value, na.rm = TRUE),
                                   mean_value = mean(value, na.rm = TRUE),
                                   nNA = sum(is.na(value)))
            dplyr::ungroup(zz)
        })
        names(res) <- gsub("\\.rds$", "", basename(res_files))
        saveRDS(res, summary_file)
    }
}
```

Assuming that the summaries have been saved for all simulation settings at
the various FDR thresholds using the code above, we load the summarized results
and merge them into a single results table.

```{r}
res <- vector("list", 10)
for (ia in 1:10) {
    imethodset <- methodset
    imethodset[which(imethodset == "ihw")] <- paste0("ihw-a", sprintf("%02d", ia))
    ires <- readRDS(paste0("allres_alpha", ia, ".rds"))
    ires <- bind_rows(ires, .id = "setting")
    ires <- dplyr::mutate(ires, dist = gsub(".*?-benchmark-(.*)", "\\1", setting),
                         setting = gsub("(.*?)-benchmark-.*", "\\1", setting))
    ires <- dplyr::filter(ires, blabel %in% imethodset)
    ires <- dplyr::mutate(ires, blabel = gsub("(-a)(.*)", "", blabel))
    res[[ia]] <- ires
}
res <- bind_rows(res)
res <- dplyr::rename(res, Method = blabel)
res <- dplyr::mutate(res, Method = gsub("-df03", "", Method))
res <- dplyr::mutate(res, Method = factor(Method, levels = gsub("-df03", "", methodset)))
```

We clean up the annotations in the table for some of the more complex simulation settings.

```{r}
res <- dplyr::mutate(res, inform = ifelse(grepl("varyinginfo", setting), dist, NA))
res <- dplyr::mutate(res, inform = as.numeric(gsub("level", "", inform)))
res <- dplyr::mutate(res, dist = ifelse(grepl("varyinginfo", setting), "gaussian", dist))

res <- dplyr::mutate(res, pi0 = ifelse(grepl("varyingpi0", setting), dist, 90))
res <- dplyr::mutate(res, pi0 = as.numeric(gsub("nullprop", "", pi0)))
res <- dplyr::mutate(res, dist = ifelse(grepl("varyingpi0", setting), "gaussian", dist))

res <- dplyr::mutate(res, signal = ifelse(grepl("varyinges", setting), dist, NA))
res <- dplyr::mutate(res, dist = ifelse(grepl("^varyinges$", setting), "gaussian", dist))
res <- dplyr::mutate(res, dist = ifelse(grepl("^varyinges-t$", setting), "t11", dist))
res <- dplyr::mutate(res, dist = ifelse(grepl("^varyinges-chisq$", setting), "chisq4", dist))
res <- dplyr::mutate(res, setting = ifelse(grepl("varyinges", setting), "varyinges", setting))
```

We also replace the sampling noise labels with more plotting-friendly labels.

```{r}
res <- dplyr::mutate(res, dist = factor(dist, levels = c("gaussian", "t11", "t5", "chisq4"),
                                        labels = c(expression("Noise: " * N(0, 1)),
                                                   expression("Noise: " * t[11]),
                                                   expression("Noise: " * t[5]),
                                                   expression("Noise: " * {chi^2}[4]))))
```

We use the standardize candy color scheme and line types for the plots.

```{r}
col <- as.character(candycols$col)
names(col) <- as.character(candycols$Method)
lty <- as.character(candycols$lty)
names(lty) <- as.character(candycols$Method)
```

There are several different simulation settings that can be investigated.

```{r}
dplyr::distinct(res, setting)
```

Namely, simulation settings were run with to investigate the impact of different
informative covariates, noninformative covariates, varying null proportions,
varying covariate informativeness, and varying effect size distributions (including
unimodal effects as described in the ASH manuscript). Many of these simulation
settings were also run with different sampling noise distributions, including
Normal/Gaussian, t with 11 degrees of freedom, t with 5 degrees of freedom, and
Chi-squared with 4 degrees of freedom.

@@

For null simulations, rather than the false discovery rate, we take a look at the true negative
rate (equivalently, the proportion of false positives) since the FDR will be 1 if any rejections
are made. Additionally, we take a look at the FWER (the proportion of simulation replicates out
of 100 with at least one rejection). In these plots, `ashq`, `scott-theoretical` and `scott-theoretical`
are excluded for the Chi-Squared simulation settings.

```{r, fig.width = 18, fig.height = 8}
res_nullset <- dplyr::filter(res, setting == "null",
                             !(Method == "ashq" & grepl("chi\\^2", dist)),
                             !(grepl("scott", Method) & grepl("chi\\^2", dist)))
res_nullset <- tidyr::complete(res_nullset, setting, Method, dist, key)

null_tnr <- dplyr::filter(res_nullset, key == "TNR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("TNR", labels = scales::percent) +
    ggtitle("Mean TNR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

null_fwer <- dplyr::filter(res_nullset, key == "FWER") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FWER", labels = scales::percent) +
    ggtitle("FWER Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

gp <- plot_grid(null_tnr + guides(color = FALSE, linetype = FALSE),
                null_fwer + guides(color = FALSE, linetype = FALSE) + coord_cartesian(ylim = c(0, .2)),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(null_tnr), rel_widths = c(1, 1/16))
gp
```

# Sampling Distributions

We just take a look at different noise distributions for a single informative covariate.

```{r, fig.width = 18, fig.height = 8}
res_noise <- dplyr::filter(res, setting == "informative-cubic")
res_noise <- tidyr::complete(res_noise, setting, Method, dist, key)

noise_fdr <- dplyr::filter(res_noise, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

noise_tpr <- dplyr::filter(res_noise, key == "TPR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("TPR", labels = scales::percent) +
    ggtitle("Mean TPR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

gp <- plot_grid(noise_fdr + guides(color = FALSE, linetype = FALSE) + coord_cartesian(ylim = c(0, .2)),
                noise_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(noise_tpr), rel_widths = c(1, 1/16))
gp
```

# Informative Covariates

We also take a look across different informative covariates.

```{r, fig.width = 18, fig.height = 8}
res_icov <- dplyr::filter(res, grepl("^informative", setting), grepl("N\\(0, 1\\)", dist))
res_icov <- tidyr::complete(res_icov, setting, Method, dist, key)

icov_fdr <- dplyr::filter(res_icov, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ setting, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

icov_tpr <- dplyr::filter(res_icov, key == "TPR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    facet_grid(. ~ setting, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("TPR", labels = scales::percent) +
    ggtitle("Mean TPR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

gp <- plot_grid(icov_fdr + guides(color = FALSE, linetype = FALSE) + coord_cartesian(ylim = c(0, .2)),
                icov_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(icov_tpr), rel_widths = c(1, 1/16))
gp
```

The general trends are identical across informative covariates considered (cubic: a monotonic relationship,
sine: a non-monotone relationship, and step: a discrete relationship).

# Noninformative Covariates

We take a look at noninformative covariates on their own.

```{r, fig.width = 18, fig.height = 8}
res_noni <- dplyr::filter(res, grepl("noninformative", setting))
res_noni <- tidyr::complete(res_noni, setting, Method, dist, key)

noni_fdr <- dplyr::filter(res_noni, key == "FDR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("FDP", labels = scales::percent) +
    ggtitle("Mean FDP Over 100 Replications (noninformative covariates)") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

noni_tpr <- dplyr::filter(res_noni, key == "TPR") %>%
    ggplot(aes(x = alpha, y = mean_value, color = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width = 0.0025, alpha=0.5) +
    facet_grid(. ~ dist, scales = "free_x", labeller = label_parsed) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) +
    scale_y_continuous("TPR", labels = scales::percent) +
    ggtitle("Mean TPR Over 100 Replications (noninformative covariates)") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

gp <- plot_grid(noni_fdr + guides(color = FALSE, linetype = FALSE) + coord_cartesian(ylim = c(0, .2)),
                noni_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(noni_tpr), rel_widths = c(1, 1/16))
gp
```

We next take a look at noninformative covariates against informative covariates.

# Noninformative vs. Informative

```{r, fig.width = 10, fig.height = 4}
res_compc <- dplyr::filter(res, grepl("informative-cubic", setting) |
                                grepl("noninformative", setting),
                           grepl("N\\(0, 1\\)", dist))
res_compc <- tidyr::complete(res_compc, setting, Method, dist, key)
res_compc <- dplyr::mutate(res_compc, lab = round(100*alpha))
res_compc <- dplyr::mutate(res_compc, lab = ifelse(lab %in% c(1, 10), lab, NA))

compc_fdr <- dplyr::filter(res_compc, key == "FDR") %>%
    dplyr::select(setting, Method, dist, alpha, lab, mean_value) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, label = lab,
               color = Method, linetype = Method)) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    geom_hline(yintercept = c(.01, .1), lty = 2, color = "blue", alpha = 1/2) + 
    geom_vline(xintercept = c(.01, .1), lty = 2, color = "blue", alpha = 1/2) + 
    geom_line(alpha = 0.85) +
    geom_text(size = 3) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("noninformative (FDP)", breaks = seq(0, 1, .02), labels = scales::percent) + 
    scale_y_continuous("informative (FDP)", breaks = seq(0, 1, .02), labels = scales::percent) + 
    ggtitle("Mean FDP Over 100 Replications") +
    expand_limits(x = 0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

compc_tpr <- dplyr::filter(res_compc, key == "TPR") %>%
    dplyr::select(setting, Method, dist, alpha, lab, mean_value) %>%
    tidyr::spread(setting, mean_value) %>%
    ggplot(aes(x = noninformative, y = `informative-cubic`, label = lab,
               color = Method, linetype = Method)) +
    geom_abline(intercept = 0, slope = 1, lty = 2, color = "blue", alpha = 1/2) + 
    geom_line(alpha = 0.85) +
    geom_text(size = 3) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("noninformative (TPR)", labels = scales::percent) + 
    scale_y_continuous("informative (TPR)", labels = scales::percent) + 
    ggtitle("Mean TPR Over 100 Replications") +
    expand_limits(x = 0, y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

gp <- plot_grid(compc_fdr + guides(color = FALSE, linetype = FALSE),
                compc_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], nrow = 1)
gp <- plot_grid(gp, get_legend(compc_tpr), rel_widths = c(1, 1/8))
gp
```

We can also plot the differences.

```{r, fig.width = 10, fig.height = 4}
compc2_fdr <- dplyr::filter(res_compc, key == "FDR") %>%
    dplyr::select(setting, Method, dist, alpha, lab, mean_value) %>%
    tidyr::spread(setting, mean_value) %>%
    dplyr::mutate(gain = `informative-cubic` - noninformative) %>%
    ggplot(aes(x = alpha, y = gain, color = Method, linetype = Method)) +
    geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2) + 
    geom_line(alpha = 0.85) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) + 
    scale_y_continuous("change in FDP", breaks = seq(-1, 1, .001), labels = scales::percent) + 
    ggtitle("Mean Change in FDP Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
